\section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}

Paper looks into the positives of secondary channels used to authenticate device pairing. Such as device fingerprint comparison. It also aims to look into the fact that many studies performed do not take into consideration the aspect of human interaction.

Total of 30 paid participants were recruited where the experiment simulated a P2P payment system.

They collected:
\begin{itemize}
    \item Time to completed the associated process
    \item Number of security or non-security related errors
\end{itemize}

And quantified using questionnaires:
\begin{itemize}
    \item Ease of use with the representation
    \item Satisfaction with time spent with a method/representation
    \item Participant's confidence with the scheme
\end{itemize}

The paper also tested methods:
\begin{itemize}
    \item Compare and Confirm
    \item Compare and Select
    \item Compare and Enter
    \item Barcode scanning
\end{itemize}

Representations:
\begin{itemize}
    \item Numerical
    \item Alphanumerical
    \item Words
    \begin{itemize}
        \item Dictionary of 1024 words each mapped to 10-bits
    \end{itemize}
    \item Sentences
    \item Images
    \item Melodies
    \item Sound (Numerical/Alphanumerical)
\end{itemize}

"People are the weakest link in the security chain" [26]

Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.

Talks about systems that were secure on paper that ended up in practice being miss-handled to reduce security. One example is with the Russian army in WWI [1]

Bruce Schneier [27] also argues that systems and involves humans therefore often systems are broken due to improper use.


\subsection{Findings}
\begin{itemize}
    \item Showed for \textbf{usability} methods ranked:
    \begin{itemize}
        \item Comparing-confirm
        \item Typing strings
        \item Comparing-select
        \item Barcode
    \end{itemize}

    \item Showed for \textbf{combined security} and \textbf{usability} methods ranked:
    \begin{itemize}
        \item Typing strings
        \item Barcodes
        \item Comparing-confirm
        \item Comparing-select
    \end{itemize}

    Showed that the best methods in terms of the SUM score [24] ranked the top 3 as:
    \begin{itemize}
        \item Numeric(C\&C)          [73.7]
        \item Alphanumerical(C\&C)   [72.5]
        \item Words (C\&C)           [70.6]
    \end{itemize}

    Numerical had 0\% security failures, Word 3.3\% and Alphanumerical had a high 13.3\% 

    NOTE: This is a very small sample size.
\end{itemize}